---
title: "assign4"
output: html_notebook
---
```{r}
library(tidyverse)
library(lubridate)
library(RVerbalExpressions)
library(stringr)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

```{r}

#Floor_date when passed with "years" as a parameter floors the date to the the first date of the year to any date passed. and when used with "+" months(0:11) and then gets first date for each month.

floor_date(today(),"years")+ months(0:11)


# Another approach

date_vector<-function(month="0",year="2019",day="01"){
 month="0"
 year="2019"
 day="01"
  dates<- rep(NA_real_,12)
  date_123<- rep(NA_real_,12)
  for(i in 1:12){
    if(i<=9){
      month<-str_c("0",i,sep="")}
    else{
    month<-i
    }
    dates[i]<- str_c(year,month,day,sep="-")
  }
for(j in 1:12){
print(ymd(dates[j]))
  
}
  date_123
}

date_vector()

```


Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
age_finder<-function(birth_date){
  date<-ymd(birth_date)
  if(as.numeric(str_c(month(today()),day(today())))>as.numeric(str_c(month(date),day(date))))
     {
    age<- year(today())-year(date) 
    }
  else{
     age<- year(today())-year(date) -1
    }
  age
}


age_finder(19970823)

```


Write a function that given your birthday, returns the day of the week you were born on.

```{r}
dayweek_bday<-function(birth_date){
  dt<-ymd(birth_date)
  wday(dt,label=TRUE,abbr = FALSE)
}

dayweek_bday(19970823)
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}

#Regular expressions
strings<-stringr::words
str_view(strings,".{7,}",match = TRUE)
str_subset(strings,".{7,}")


#Verbal expressions

 x<-rx() %>% 
  rx_start_of_line() %>% 
  rx_alpha() %>% 
  rx_multiple(min=7) %>% 
   rx_end_of_line()
 
 str_view(strings,x,match=TRUE)
   
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
#Regular expressions
words[str_detect(strings,"^[^aieouAIEOU]+$")]
words[str_detect(strings,"[aieouAIEOU]+",negate = TRUE )]

# Verbal expressions
x<-rx() %>% 
   rx_start_of_line() %>% 
  rx_anything_but("aieouAIEOU") %>% 
  rx_multiple(min=1) %>% 
  rx_end_of_line()
str_detect(strings,x)
```


Empirically verify the rule “i before e except after c”.
```{r}
#Regular expressions
#words which follow rule
strings[str_detect(strings,"[^c]ie")]

#verbal expressions
x<-rx() %>%  
  rx_avoid_prefix("c") %>% 
  rx_find("ie") 
 

strings[str_detect(strings,x)]

  

```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}

#Regular expression
"^{3}[-]{3}[-]{4}$"
"^{3}[.]{3}[.]{4}$"

#Verbal expression
phone_num<-rx() %>% 
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line()

```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

